### 2017-11-26 TeX/NeuralNetwork_1.tex
Updates from ShareLaTeX

@@

    % Draw the output layer node
    \node[output neuron,pin={[pin edge={->}]right:$\left(+\;a\;b\right)$}, right of=H-3] (O) {\texttt{eval(}$\left(+\;a\;b\right)$\texttt{)}};

@@

\includegraphics[scale=1]{Visuals/NeuralNetwork_1_NetworkTree.ps} \\

This tree-like structure closely mimics the abstract syntax tree which is generated by compilers when processing code in a program. For example, to evaluate the results of the expressions "+ 5 4" and "- 5 4", a compiler may generate the following trees: \\

\includegraphics[scale=1]{Visuals/NeuralNetwork_1_SyntaxTree.ps}

>>>>

\usepackage{tikz, xcolor}

@@

    % Draw the output layer node
    \node[output neuron,pin={[pin edge={->}]right:$\left(+\;a\;b\right)$}, right of=H-3] (O) {\textt{eval(}$\left(+\;a\;b\right)$\textt{)}};

@@

\includegraphics{Visuals/NeuralNetwork_1_SyntaxTree.pdf}

This structure is very similar to how compilers/interpreters view and evaluate code in a program.

### 2017-11-26 TeX/Preface.tex
Updates from ShareLaTeX

	The purpose of our research is to understand how Artificial Neural Networks can support multiple classes of computations. This document will contain notes, diagrams, and explantations pertaining to each of the experiments we will conduct to investigate this problem. Code for each subsection of this document can be found at \url{https://github.com/DariusBxsci/NeuralNetworkResearch/tree/master/NeuralNets}.

>>>>

    \begin{enumerate}
        \item What is symbolic computation?
        \item What is calculation?
        \item What is meant by a computational class?
    \end{enumerate}

     Code for each subsection of this document can be found at \url{https://github.com/DariusBxsci/NeuralNetworkResearch/tree/master/NeuralNets}.
